---
title: "regex_problems"
author: "Colleen Minnihan"
date: "4/10/2021"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
```


```{r}
# read in the data
bestsellers <- read.csv("bestsellers.csv") # the filepath to the downloaded data

bestsellers %>%
  head(10)
```

1. Find books with multiple authors (HINT: Consider the possibility of an author having “and” in their name)
```{r}
#how do i get it to print the book titles?
str_extract(bestsellers %>% pull(author), " and ")
```

2. Detect if the author’s first name starts with a vowel
```{r}
str_detect(bestsellers %>% pull(author), "^[AEIOUY]")
```

3. Change all authors with the name Alexander to Alex
```{r}
str_replace_all(bestsellers %>% pull(author), "Alexander", "Alex")
```

4. Find books that are the second book in a series
```{r}
bestsellers %>%
  mutate(series = str_detect(bestsellers %>% pull(description), pattern = "sequel")) %>%
  filter(series == TRUE)
```

5. Find books that are the third or fourth one in a series
```{r}
bestsellers %>%
  mutate(series = str_detect(bestsellers %>% pull(description), pattern = "third|fourth")) %>%
  filter(series == TRUE)

head(bestsellers)
```
6.
```{r}
bestsellers %>%
  mutate(series = str_detect(bestsellers %>% pull(description), pattern = "[10-19]th")) %>%
  filter(series == TRUE)
```

7. Describe in your own words how you would go about writing a regular expression for password pattern matching (ie 8 character minimum, one capital letter minimum, one lowercase letter minimum, one digit minimum, one special character minimum). This is an open ended question.

**How do I do this in paragraph form and not attempt to write the regular expression?**


